\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

%%%%%%%%%%%%
\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}

@@

\KCnote{\blue{need to put screenshots from pseudo hele-shaw case - log on to Jeff's station and then include the following cases}}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase}
\end{figure}

%\begin{figure}[h]
%\begin{center}
%\centering
%\subfigure[MR100 fixed mesh t=500]{%
%\label{fig:}
%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
%}%
%\subfigure[MR100 fixed mesh t=1500]{%
%\label{fig:}
%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
%}%
%\subfigure[MR100 fixed mesh t=3000]{%
%\label{fig:}
%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
%}\\ 
%\subfigure[MR100 fixed mesh end]{%
%\label{fig:}
%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
%}\\
%\end{center}
%\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
%\label{fig:4testcase}
%\end{figure}

\begin{figure}[h] 
\begin{center}
\subfigure[MR1]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR1.pdf}
}%
\subfigure[Recovery for MR1]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR10.pdf}
}%
\subfigure[Recovery for MR10]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.pdf}
}\\
\subfigure[MR100]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.pdf}
}%
\subfigure[Recovery for MR100]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.pdf}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates. The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}. }
\label{fig:recoveryrates}
\end{figure}

>>>>

%%%%%%%%%%%%
\subsection{\blue{title for the $3$ hell shaw cases}}

%\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}

At this point we have to mentioned one more set of simulations, based on the work of \citet{saffman_1986}. The Hele-shaw cell geometrical domain as this is defined by experimental studies and is presented in figures \ref{{fig:1a_homoheleshaw_3},{fig:1b_homoheleshaw_3}} and fig. \ref{fig:1c_homoheleshaw_3} is used. In all cases, simulations were performed in a squared geometry of $5x5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 (i.e., sqrt(2*0.25)). The sink (represented by 0 pressure BC) is allocated in the top right hand side corner of the domain. Newmann BC (i.e., no flux) was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter homogeneous and heterogeneous domain is used.

\begin{figure}
\centering
\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}}\\[2mm]%
\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}}%
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in fig.\ref{fig:1b_homoheleshaw_3} and fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}\\[2mm]%
\subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
\caption{As the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=3500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf}}\\[2mm]%
\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}%
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}}\\[2mm]%
\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}}%
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_3}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}\\[2mm]%
\subfigure[flow at t=4000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}}%
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}}\\[2mm]%
\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}%
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}}\\[2mm]%
\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}}%
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_3}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=2000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf}}\\[2mm]%
\subfigure[flow at t=3000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}}%
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}}\\[2mm]%
\subfigure[flow at t=24000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}}%
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}

@@

@@

\begin{figure}
%\centering
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase}
\end{figure}

\begin{comment}
\begin{figure}[h] 
\begin{center}
\subfigure[MR1]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR1.pdf}
}%
\subfigure[Recovery for MR1]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR10.pdf}
}%
\subfigure[Recovery for MR10]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.pdf}
}\\
\subfigure[MR100]{%
\label{fig:}
\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.pdf}
}%
\subfigure[Recovery for MR100]{%
\label{fig:}
\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.pdf}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates. The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}. }
\label{fig:recoveryrates}
\end{figure}
\end{comment}
